Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2022-01-11 Supplemental-Material-B-Annotated-Analysis.Rmd
SI B worker zwc

# Load Custom Packages
source("./scripts/functions/fun.panel.R")
source("./scripts/functions/themes.R")
source("./scripts/functions/binaryCor.R")
source("./scripts/functions/MlCorMat.R")

@@

<i class="fas fa-exclamation-circle"></i> Note. Multilevel effect size could be: 
\begin{equation}
(\#eq:MlEffectSize)
f_b^2 = \frac{R_{ab}^2 - R_a^2}{1 - R_{ab}^2} \\
R^2 = \frac{V_{null} - V_{model}}{V_{null}} \\
f_b^2 = \frac{\frac{V_{null} - V_{ab}}{V_{null}} - \frac{V_{null} - V_{a}}{V_{null}}}{1 - \frac{V_{null} - V_{ab}}{V_{null}}}
\end{equation}

@@

warning(
  "some variable transformations (esp. _c and _z) might be across all participants (i.e., not within PP)."
)

@@

# Between participants contact frequency
workerContactFreq <- dtWorker$full %>%
  group_by(ExternalReference) %>%
  summarise(
    n = n(),
    SumContactNL = sum(Contact_dum),
    PercContactNL = SumContactNL / n * 100,
    SumContactNLAll = sum(number),
    AvAttitude = mean(thermometerDutch_1, na.rm = T)
  ) %>%
  mutate(
    WinSumContactNL = DescTools::Winsorize(SumContactNL),
    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
  )

@@

@@

>>>>

# Load Custom Packages
source("./scripts/functions/fun.panel.R")
source("./scripts/functions/themes.R")
source("./scripts/functions/binaryCor.R")
source("./scripts/functions/MlCorMat.R")
source("./scripts/functions/MlTbl.R")
source("./scripts/functions/metaLmer.R")

@@

<!-- <i class="fas fa-exclamation-circle"></i> Note. Multilevel effect size could be:  -->
<!-- \begin{equation} -->
<!-- (\#eq:MlEffectSize) -->
<!-- f_b^2 = \frac{R_{ab}^2 - R_a^2}{1 - R_{ab}^2} \\ -->
<!-- R^2 = \frac{V_{null} - V_{model}}{V_{null}} \\ -->
<!-- f_b^2 = \frac{\frac{V_{null} - V_{ab}}{V_{null}} - \frac{V_{null} - V_{a}}{V_{null}}}{1 - \frac{V_{null} - V_{ab}}{V_{null}}} -->
<!-- \end{equation} -->

<!-- <br/> -->

@@

warning(
  "some variable transformations (esp. _c and _z) might be across all participants (i.e., not within PP). See next step."
)

@@

@@

# Create variables centered and standardized within Participant
# i.e., divide into trait and state
workerWithinBetween <-
  MlTraitState(
    data = workerInteractionType,
    id = "PID",
    selection =
      c(
        "keyMotiveFulfilled",
        "competence.daily.all",
        "autonomy.daily.all",
        "relatedness.daily.all",
        "thermometerDutch_1",
        "keymotive_fulfillemt_1",
        "competence_1",
        "autonomy_1",
        "relatedness_1", 
        "quality_overall_1", 
        "OutgroupInteraction",
        "NonOutgroupInteraction"
      )
  )

workerOutWithinBetween <-
  MlTraitState(
    data = workerInteractionType %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection =
      c(
        "keyMotiveFulfilled",
        "thermometerDutch_1",
        "keymotive_fulfillemt_1",
        "competence_1",
        "autonomy_1",
        "relatedness_1", 
        "quality_overall_1"
      )
  )

# Between participants contact frequency
workerContactFreq <- dtWorker$full %>%
  group_by(PID) %>%
  summarise(
    n = n(),
    SumContactNL = sum(Contact_dum),
    PercContactNL = SumContactNL / n * 100,
    SumContactNLAll = sum(number),
    AvAttitude = mean(thermometerDutch_1, na.rm = T)
  ) %>%
  mutate(
    WinSumContactNL = DescTools::Winsorize(SumContactNL),
    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
  )

@@

```{r WorkerVarDescr}

workerMlCor <-
  MlCorMat(
    data = dtWorkerSupp$workerInteractionType,
    id = "PID",
    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "quality_overall_1", "thermometerDutch_1"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
  )

workerMlCor %>%
  kable(
    .,
    caption = "Worker: Multilevel Core Variable Descriptives",
    format = "latex",
    booktabs = TRUE,
    linesep = linesep(c(ncol(.))),
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/workerVarDescr.tex")
